---
title: "Complex_anchor_emma_200507"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 120),
  message = FALSE,
  warning = FALSE
)
```

  
```{r}
# Load required packages

library(Seurat)
library(dplyr)
#library(Matrix)
library(readr)
#library(reshape2)
library(ggplot2)
library(cowplot)
library(gplots)
library(RColorBrewer)
library(sctransform)
#library(patchwork)

```



```{r seuratobjects_to_singleobject}

#

Complex009D0.data <- read.table("N702_B_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

#Complex009D0.data <- read.table("~/Documents/scRNA/Tom_hg38/N702_B/N702_B_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

Complex009D0.data <- Complex009D0.data[,1:800]

Complex009D0_B2 <- CreateSeuratObject(counts = Complex009D0.data, min.cells = 3, min.features = 200, project = "Organoid_DropSeq", meta.data = data.frame(Treatment = rep("Complex009D0",ncol(Complex009D0.data)), row.names = colnames(Complex009D0.data)))


#

Complex009D4.data <- read.table("N704_D_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

#Complex009D4.data <- read.table("~/Documents/scRNA/Tom_hg38/N704_D/N704_D_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

Complex009D4.data <- Complex009D4.data[,1:800]

Complex009D4_D2 <- CreateSeuratObject(counts = Complex009D4.data, min.cells = 3, min.features = 200, project = "Organoid_DropSeq", meta.data = data.frame(Treatment = rep("Complex009D4",ncol(Complex009D4.data)), row.names = colnames(Complex009D4.data)))


#

Complex009D4Dasa.data <- read.table("N705_E_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

#Complex009D4Dasa.data <- read.table("~/Documents/scRNA/Tom_hg38/N705_E/N705_E_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

Complex009D4Dasa.data <- Complex009D4Dasa.data[,1:800]

Complex009D4Dasa_E2 <- CreateSeuratObject(counts = Complex009D4Dasa.data, min.cells = 3, min.features = 200, project = "Organoid_DropSeq", meta.data = data.frame(Treatment = rep("Complex009D4Dasa",ncol(Complex009D4Dasa.data)), row.names = colnames(Complex009D4Dasa.data)))


##

Complex016D0.data <- read.table("N707_G_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

#Complex016D0.data <- read.table("~/Documents/scRNA/Tom_hg38/N707_G/N707_G_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

Complex016D0.data <- Complex016D0.data[,1:800]

Complex016D0_G2 <- CreateSeuratObject(counts = Complex016D0.data, min.cells = 3, min.features = 200, project = "Organoid_DropSeq", meta.data = data.frame(Treatment = rep("Complex016D0",ncol(Complex016D0.data)), row.names = colnames(Complex016D0.data)))


#

Complex016D4.data <- read.table("N709_I_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

#Complex016D4.data <- read.table("~/Documents/scRNA/Tom_hg38/N709_I/N709_I_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

Complex016D4.data <- Complex016D4.data[,1:800]

Complex016D4_I2 <- CreateSeuratObject(counts = Complex016D4.data, min.cells = 3, min.features = 200, project = "Organoid_DropSeq", meta.data = data.frame(Treatment = rep("Complex016D4",ncol(Complex016D4.data)), row.names = colnames(Complex016D4.data)))


#

Complex016D4Dasa.data <- read.table("N710_J_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

#Complex016D4Dasa.data <- read.table("~/Documents/scRNA/Tom_hg38/N710_J/N710_J_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

Complex016D4Dasa.data <- Complex016D4Dasa.data[,1:800]

Complex016D4Dasa_J2 <- CreateSeuratObject(counts = Complex016D4Dasa.data, min.cells = 3, min.features = 200, project = "Organoid_DropSeq", meta.data = data.frame(Treatment = rep("Complex016D4Dasa",ncol(Complex016D4Dasa.data)), row.names = colnames(Complex016D4Dasa.data)))


##

Complex018D0.data <- read.table("N707_L_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

#Complex018D0.data <- read.table("~/Documents/scRNA/Tom_hg38/N707_L/N707_L_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

Complex018D0.data <- Complex018D0.data[,1:800]

Complex018D0_L2 <- CreateSeuratObject(counts = Complex018D0.data, min.cells = 3, min.features = 200, project = "Organoid_DropSeq", meta.data = data.frame(Treatment = rep("Complex018D0",ncol(Complex018D0.data)), row.names = colnames(Complex018D0.data)))


#

Complex018D4.data <- read.table("N709_N_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

#Complex018D4.data <- read.table("~/Documents/scRNA/Tom_hg38/N709_N/N709_N_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

Complex018D4.data <- Complex018D4.data[,1:800]

Complex018D4_N2 <- CreateSeuratObject(counts = Complex018D4.data, min.cells = 3, min.features = 200, project = "Organoid_DropSeq", meta.data = data.frame(Treatment = rep("Complex018D4",ncol(Complex018D4.data)), row.names = colnames(Complex018D4.data)))


#

Complex018D4Dasa.data <- read.table("N710_O_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

#Complex018D4Dasa.data <- read.table("~/Documents/scRNA/Tom_hg38/N710_O/N710_O_STAMPS_2000.dge.txt.gz", "\t", header=T, row.names=1)

Complex018D4Dasa.data <- Complex018D4Dasa.data[,1:800]

Complex018D4Dasa_O2 <- CreateSeuratObject(counts = Complex018D4Dasa.data, min.cells = 3, min.features = 200, project = "Organoid_DropSeq", meta.data = data.frame(Treatment = rep("Complex018D4Dasa",ncol(Complex018D4Dasa.data)), row.names = colnames(Complex018D4Dasa.data)))

rm(Complex009D0.data,Complex009D4.data,Complex009D4Dasa.data,Complex016D0.data,Complex016D4.data,Complex016D4Dasa.data,Complex018D0.data,Complex018D4.data,Complex018D4Dasa.data)

```

```{r}

ComplexOrganoids <- merge(x = Complex009D0_B2, y = c(Complex009D4_D2,Complex009D4Dasa_E2,Complex016D0_G2,Complex016D4_I2,Complex016D4Dasa_J2,Complex018D0_L2,Complex018D4_N2,Complex018D4Dasa_O2), project = "Organoid_DropSeq")

rm(Complex009D0_B2,Complex009D4_D2,Complex009D4Dasa_E2,Complex016D0_G2,Complex016D4_I2,Complex016D4Dasa_J2,Complex018D0_L2,Complex018D4_N2,Complex018D4Dasa_O2)
```

```{r}

ComplexOrganoids <- SetIdent(object = ComplexOrganoids, value = "Treatment")
```

```{r}
ComplexOrganoids$patient <- plyr::mapvalues(
    x = ComplexOrganoids$Treatment, 
    from = c("Complex009D0", "Complex009D4", "Complex009D4Dasa", "Complex016D0", "Complex016D4", "Complex016D4Dasa","Complex018D0", "Complex018D4", "Complex018D4Dasa"), 
    to = c(rep("20-009",3), rep("20-016",3), rep("20-018",3))
)

head(ComplexOrganoids[[]])
```

```{r}

ComplexOrganoids[["percent.mt"]] <- PercentageFeatureSet(object=ComplexOrganoids, pattern ="^MT-")
```

####Visualize QC metrics

Quality control metrics are viewed in a violin plot to assess the data.  QC metrics are used to filter the data, removing extreme counts (representing cell doublets or ambient RNA) and cells with a high proportion of mitochondrial transcripts (representing dead/dying cells).

```{r Vln nFeature_RNA}

pdf("ComplexOrganoids_Vln_nFeature_RNA_20200507.pdf", useDingbats = FALSE)

VlnPlot(object=ComplexOrganoids, features="nFeature_RNA", pt.size = 0.05) + theme(legend.position = 'none')

dev.off()
```

```{r Vln nCount_RNA} 

pdf("ComplexOrganoids_Vln_nCount_RNA_20200507.pdf", useDingbats = FALSE)

VlnPlot(object=ComplexOrganoids, features="nCount_RNA", pt.size = 0.05) + theme(legend.position = 'none')

dev.off()
```

```{r Vln percent.mt}

pdf("ComplexOrganoids_Vln_percentmt_20200507.pdf", useDingbats = FALSE)

VlnPlot(object=ComplexOrganoids, features="percent.mt", pt.size = 0.05) + theme(legend.position = 'none')

dev.off()
```
FeatureScatter was used to examine the relationships between features (nCount_RNA vs. percent.mito and nCount_RNA vs. nFeature_RNA).

```{r feature_scatter}
# FeatureScatter is typically used to visualize feature-feature relationships, but can be used
# for anything calculated by the object, i.e. columns in object metadata, PC scores etc.

plot1 <- FeatureScatter(object = ComplexOrganoids, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(object = ComplexOrganoids, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

pdf("ComplexOrganoids_FeatureScatter_20200507.pdf", useDingbats = FALSE)

CombinePlots(plots = list(plot1, plot2), legend = 'bottom')

dev.off()
```

```{r}

ComplexOrganoids <- subset(x = ComplexOrganoids, subset = nFeature_RNA > 50 & nFeature_RNA < 5000 & percent.mt < 5)

```


```{r}

ComplexOrganoids.list <- SplitObject(ComplexOrganoids, split.by = "patient")
ComplexOrganoids.list <- ComplexOrganoids.list[c("20-009","20-016","20-018")]

```

```{r}

for (i in 1:length(ComplexOrganoids.list)) {
    ComplexOrganoids.list[[i]] <- NormalizeData(ComplexOrganoids.list[[i]], verbose = FALSE)
    ComplexOrganoids.list[[i]] <- FindVariableFeatures(ComplexOrganoids.list[[i]], selection.method = "vst", nfeatures = 2000, verbose = FALSE)
}

```

```{r}

ComplexOrganoids.anchors <- FindIntegrationAnchors(object.list = ComplexOrganoids.list, dims = 1:30)

```

```{r}

ComplexOrganoids.integrated <- IntegrateData(anchorset = ComplexOrganoids.anchors, dims = 1:30)

```

```{r}

rm(ComplexOrganoids,ComplexOrganoids.anchors,ComplexOrganoids.list,plot1,plot2)

```

```{r cell cycle scoring}

# Also read in a list of cell cycle markers, from Tirosh et al, 2015

cc.genes <- readLines(con = "./regev_lab_cell_cycle_genes.txt")

#cc.genes <- readLines(con = "~/Documents/OldMac/MacBook2017/DropSeq/cell_cycle_vignette_files/regev_lab_cell_cycle_genes.txt")

# We can segregate this list into markers of G2/M phase and markers of S
# phase
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:98]

ComplexOrganoids.integrated <- CellCycleScoring(object = ComplexOrganoids.integrated, s.features = s.genes, g2m.features = g2m.genes, set.ident = TRUE)

# view cell cycle scores and phase assignments
head(x = ComplexOrganoids.integrated[[]])
```

```{r}


# switch to integrated assay. The variable features of this assay are automatically
# set during IntegrateData
DefaultAssay(ComplexOrganoids.integrated) <- "integrated"

# Run the standard workflow for visualization and clustering
ComplexOrganoids.integrated <- ScaleData(ComplexOrganoids.integrated, verbose = FALSE)

ComplexOrganoids.integrated <- RunPCA(ComplexOrganoids.integrated, npcs = 30, verbose = FALSE)

DimHeatmap(ComplexOrganoids.integrated, dims = 1:15, cells = 500, balanced = TRUE)

ElbowPlot(object = ComplexOrganoids.integrated)
```

```{r}
ComplexOrganoids.integrated <- FindNeighbors(object = ComplexOrganoids.integrated, dims = 1:15)

ComplexOrganoids.integrated <- FindClusters(object = ComplexOrganoids.integrated, resolution = 0.4)
```

```{r}
head(x=Idents(object=ComplexOrganoids.integrated),5)
```

```{r}
ComplexOrganoids.integrated <- RunUMAP(ComplexOrganoids.integrated, reduction = "pca", dims = 1:15)
p1 <- DimPlot(ComplexOrganoids.integrated, reduction = "umap", group.by = "Treatment")

pdf("ComplexOrganoids_integrated_UMAP_Treatment_20200507.pdf", useDingbats = FALSE)

plot(p1)

dev.off()

p2 <- DimPlot(ComplexOrganoids.integrated, reduction = "umap", group.by = "patient")

pdf("ComplexOrganoids_integrated_UMAP_patient_20200507.pdf", useDingbats = FALSE)

plot(p2)

dev.off()

p3 <- DimPlot(ComplexOrganoids.integrated, reduction = "umap", group.by = "Phase")

pdf("ComplexOrganoids_integrated_UMAP_Phase_20200507.pdf", useDingbats = FALSE)

plot(p3)

dev.off()


p4 <- DimPlot(ComplexOrganoids.integrated, reduction = "umap", label = TRUE)

pdf("ComplexOrganoids_integrated_UMAP_cluster_20200507.pdf", useDingbats = FALSE)

plot(p4)

dev.off()

rm(p1,p2,p3,p4)

```

```{r}

p1 <- FeaturePlot(ComplexOrganoids.integrated,features="nFeature_RNA")
p2 <- FeaturePlot(ComplexOrganoids.integrated,features="nCount_RNA")
p3 <- FeaturePlot(ComplexOrganoids.integrated,features="percent.mt")

pdf("ComplexOrganoids_integrated_QCfeatures_20200507.pdf", useDingbats = FALSE)

CombinePlots(plots = list(p1,p2,p3), ncol = 1)

dev.off()

rm(p1,p2,p3)

```

```{r Find Markers}
# find markers for every cluster compared to all remaining cells, report
# only the positive ones
ComplexOrganoids.integrated.markers <- FindAllMarkers(object = ComplexOrganoids.integrated, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25)
ComplexOrganoids.integrated.markers %>% group_by(cluster) %>% top_n(5, avg_logFC)

write.table(ComplexOrganoids.integrated.markers, file = "ComplexOrganoids_integrated_allmarkers_20200507.txt")
```

```{r Top10 Markers}
ComplexOrganoids.integrated.top10 <- ComplexOrganoids.integrated.markers %>% group_by(cluster) %>% top_n(10, avg_logFC)
# setting slim.col.label to TRUE will print just the cluster IDS instead of
# every cell name

pdf("ComplexOrganoids_integrated_top10heatmap.pdf", useDingbats = FALSE)

DoHeatmap(object = ComplexOrganoids.integrated, features = ComplexOrganoids.integrated.top10$gene, size = 3, angle = 0) + theme(text = element_text(size = 4), legend.key.height = unit(0.2,"cm"))

dev.off()

write.table(ComplexOrganoids.integrated.top10, file = "ComplexOrganoids.integrated_top10.txt")

```


```{r}
saveRDS(ComplexOrganoids.integrated, "ComplexOrganoids_integrated_20200507.rds")
```

```{r}
ComplexOrganoids.integrated.CellType <- ComplexOrganoids.integrated@meta.data$seurat_clusters

ComplexOrganoids.integrated@meta.data$CellType <- plyr::mapvalues(ComplexOrganoids.integrated.CellType, from=c(1,4:6,8,0,2:3,7,9,10),to=c(rep("EpC",5),rep("Stroma",5),"Ciliated"))

```

```{r}
ComplexOrganoids.integrated.Condition <- ComplexOrganoids.integrated@meta.data$old.ident

ComplexOrganoids.integrated@meta.data$Condition <- plyr::mapvalues(ComplexOrganoids.integrated.Condition, from=c("Complex009D0", "Complex016D0","Complex018D0","Complex009D4", "Complex016D4","Complex018D4","Complex009D4Dasa", "Complex016D4Dasa","Complex018D4Dasa"),to=c(rep("ComplexD0",3),rep("ComplexD4",3), rep("ComplexD4Dasa",3)))

```

```{r}
#Subset the data by CellType

#Set idents to CellType for subsetting
ComplexOrganoids.integrated <- SetIdent(ComplexOrganoids.integrated,value="CellType")

ComplexOrganoids.integrated_EpC <- subset(ComplexOrganoids.integrated, idents = "EpC")

saveRDS(ComplexOrganoids.integrated_EpC, file = "CellType_EpC_Complex.rds")

ComplexOrganoids.integrated_Stroma <- subset(ComplexOrganoids.integrated, idents = "Stroma")

saveRDS(ComplexOrganoids.integrated_Stroma, file = "CellType_Stroma_Complex.rds")
```


```{r}
#Subset the data by Condition for CellPhoneDB

#Set idents to CellType for subsetting
ComplexOrganoids.integrated <- SetIdent(ComplexOrganoids.integrated,value="Condition")

ComplexOrganoids.integrated_D0 <- subset(ComplexOrganoids.integrated, idents = "ComplexD0")

saveRDS(ComplexOrganoids.integrated_D0, file = "Condition_D0_Complex.rds")

ComplexOrganoids.integrated_D4 <- subset(ComplexOrganoids.integrated, idents = "ComplexD4")

saveRDS(ComplexOrganoids.integrated_D4, file = "Condition_D4_Complex.rds")

ComplexOrganoids.integrated_D4Dasa <- subset(ComplexOrganoids.integrated, idents = "ComplexD4Dasa")

saveRDS(ComplexOrganoids.integrated_D4Dasa, file = "Condition_D4Dasa_Complex.rds")
```
